\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-20 pldi/draft.tex
Add parallel figure

First of all, \sys without the \ttt{eager} optimization enabled
performs comparably with \ttt{sort -{}-parallel}. On the other hand,
enabling the \ttt{eager} optimization allows \sys to perform much
better ($\sim 2$ times) than \ttt{sort} with the \ttt{-{}-parallel}
flag. That is because \sys with the \ttt{eager} optimization enabled
essentially uses intermediate buffers (on disk) between the merge
phases.
%% On the other hand, \ttt{sort --parallel} sorts the input trying to
%% minimize additional memory (so doesn't allocate intermediate
%% buffers).
%% %% \kk{If we want, we can add here numbers where we allow sort --parallel
%% %%   to use additional ram for intermediate buffers (using the -S flag).}
%% Of course, it would be possible to manually create a longer pipeline
%% and use intermediate buffers to speed this up, but this defeats the
%% purpose of having a simple solution.

Second, based on the comparison with \ttt{sort --parallel} it seems
that the scaleup limit that \sys reaches with sort is \todo{inherent
  and cannot be overpassed} \kk{We have to find a way to argue for the
  previous statement}. Because of that, all pipelines and scripts that
contain \ttt{sort} in our evaluation (several one-liners and unix50)
have this upper bound on scalability. \kk{Maybe move this paragraph in
  the one-liners section.}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{\detokenize{./figs/sort_baseline_comparison_scaleup.pdf}}
  \caption{ \textbf{Comparison with \ttt{sort -{}-parallel}.}
  }
  \vspace{-15pt}
  \label{fig:sort-parallel-comparison}
\end{figure}

>>>>

First of all, \sys without the \ttt{eager} optimization enabled
performs comparably with \ttt{sort -{}-parallel}. On the other hand,
enabling the \ttt{eager} optimization allows \sys to perform much
better ($\sim 2$ times) than \ttt{sort} with the \ttt{-{}-parallel}
flag. That is because \sys with the \ttt{eager} optimization enabled
essentially uses intermediate buffers (on disk) between the merge
phases.
%% On the other hand, \ttt{sort --parallel} sorts the input trying to
%% minimize additional memory (so doesn't allocate intermediate
%% buffers).
%% %% \kk{If we want, we can add here numbers where we allow sort --parallel
%% %%   to use additional ram for intermediate buffers (using the -S flag).}
%% Of course, it would be possible to manually create a longer pipeline
%% and use intermediate buffers to speed this up, but this defeats the
%% purpose of having a simple solution.
\begin{wrapfigure}{r}{0.25\textwidth}
  \begin{center}
    \includegraphics[width=0.25\textwidth]{\detokenize{./figs/sort_baseline_comparison_scaleup.pdf}}
  \end{center}
%   \vspace{-15pt}
% \caption{ \textbf{Comparison with \ttt{sort -{}-parallel}.} }
\end{wrapfigure}
Second, based on the comparison with \ttt{sort --parallel} it seems
that the scaleup limit that \sys reaches with sort is \todo{inherent
  and cannot be overpassed} \kk{We have to find a way to argue for the
  previous statement}. Because of that, all pipelines and scripts that
contain \ttt{sort} in our evaluation (several one-liners and unix50)
have this upper bound on scalability. \kk{Maybe move this paragraph in
  the one-liners section.}

@@
